---
output: 
  github_document:
    html_preview: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

## shinyhydat

<div id="devex-badge"><a rel="Inspiration" href="https://github.com/BCDevExchange/docs/blob/master/discussion/projectstates.md"><img alt="An idea being explored and shaped. Open for discussion, but may never go anywhere." style="border-width:0" src="https://assets.bcdevexchange.org/images/badges/inspiration.svg" title="An idea being explored and shaped. Open for discussion, but may never go anywhere." /></a></div>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```



This is a shiny app to view and download historical streamflow data from a downloaded HYDAT SQLite database and real-time data using [tidyhydat](https://github.com/ropensci/tidyhydat).

## Setup
These instructions assume that you have [installed R and RStudio](https://github.com/bcgov/bcgov-data-science-resources/wiki/Installing-R-&-RStudio) already on your computer.

### Package downloads
The first step to getting the shinyhydat up and running on your machine is to download all the packages needed by the shiny app. All of these packages are available on CRAN with the exception of `tidyhydat`. Type the following into R console to install all of them:
```{r pcks, eval=FALSE, echo=TRUE}
install.packages("tidyhydat")
install.packages("shinydashboard")
install.packages("leaflet")
install.packages("plotly")
install.packages("devtools")
install.packages("shinyWidgets")

devtools::install_version("shiny", version = "1.0.3") # 1.0.3 shiny
```

### HYDAT download
The second step to using the shinyhydat is to download a version of the HYDAT database, Environment and Climate Change Canada's comprehensive database of historical hydrometric data. The `tidyhydat` package provides a convenience function to download HYDAT (be patient though this takes a long time!):
```{r, eval=FALSE}
tidyhydat::download_hydat()
```

tidyhydat functions will automatically know where to look for HYDAT if you download HYDAT using this function.

## Usage

- Open app.R file in RStudio and run the app.


### License

    Copyright 2017 Province of British Columbia

    Licensed under the Apache License, Version 2.0 (the "License");
    you may not use this file except in compliance with the License.
    You may obtain a copy of the License at 

       http://www.apache.org/licenses/LICENSE-2.0

    Unless required by applicable law or agreed to in writing, software
    distributed under the License is distributed on an "AS IS" BASIS,
    WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
    See the License for the specific language governing permissions and
    limitations under the License.
